Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-12-14 latex/ms.tex
modify caption of Fig1 in main text

In the example depicted in {\bf Fig~\ref{cartoon}b}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed. In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explain the next section. In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs. The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).

@@

\newcommand{\figcapa}{(a) The phases of the events relevant to this study along the time line. (b) Example of relationships between parents and their offspring number between/within populations. Upper and lower square indicates individuals belonging to the population 1 before migrations (at sample timing in the first year) and individuals belonging to the population 2 after reproduction (at sample timing in the second year), respectively. The open circles on the left side, right side, and the center represent mothers, fathers, and their offspring, respectively. The thin line denotes parent-offspring relationship. The bold arrow denotes the migration and the symbol x denotes a failure to survive at sampling in the second year. The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$, $H_{\rm HS, bet}=2$, $H_{\rm PO, 1}=3$, and $H_{\rm PO, 2}=2$.}

>>>>

In the example depicted in {\bf Fig~\ref{cartoon}b}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed. In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explained in the following section. In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs. The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).

@@

\newcommand{\figcapa}{(a) The phases of the events relevant to this study along the time line. (b) Hypothetical populations with $N_{1}=16$, $N_{2}=14$, and $M=6$. Upper and lower square indicates individuals belonging to the population 1 before migration (at sample timing in the first year) and individuals belonging to the population 2 after reproduction (at sample timing in the second year), respectively. The open circles on the left side, right side, and the center represent mothers, fathers, and their offspring, respectively. The thin line denotes parent-offspring relationship. The bold arrow denotes the migration and the symbol x denotes a failure to survive at sampling in the second year. Sampled individuals are labeled with an index number. The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$ (i.e., ``7-10'' pair), $H_{\rm HS, bet}=2$ (i.e., ``8-16'' and ``9-16'' pairs), $H_{\rm PO, 1}=3$ (i.e., ``1-6'', ``3-5'' and ``4-7'' pairs), and $H_{\rm PO, 2}=2$ (i.e., ``11-17'' and ``15-16'' pairs).}
